When are Fuzzy Extractors Possible?

### 2014-12-01 constantRate/eurocryptReviewResponse.txt

Thank you for the reviews and feedback.  We will incorporate your comments into our work.

Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
A: The second and third construction also secure different types of sources.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction allows all blocks to be determined by a single block as long as most blocks are hard to guess.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is known as a robust fuzzy extractor (Boyen et al., Eurocrypt 2004).  It is a separate question than reusability of a fuzzy extractor. Robust fuzzy extractors are easy in the random oracle model.  In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).

Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.  Is it a hard challenge to find an alternative of removing this condition? 
Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources
(biometric, PUF examples) where standard fuzzy extractors fail? It would be
great to gain intuition about whether these construction can be improved or
not.
A: The second construction provides reusability regardless of alphabet size.  (It only corrects more errors than entropy on a super-constant size alphabet.)  The constructions support different types of sources, the reusable construction does support a superset of the information-theoretic construction.

Supporting more errors than entropy on a constant size alphabet remains a challenge.  As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.  This is to avoid stronger lower bounds that arise when working on a single space.  Known techniques for working on a single space recover the original reading (known as a secure sketch) and are subject to stronger negative results.  It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.

We have run some initial experiments and the second construction appears promising for irises where the distance is binary Hamming over 2048 bit strings.  However, there is still considerable work to verify that irises the second construction is secure on irises.  The main work is showing that  sampling producing high entropy strings.  Indeed, the main barrier to applicability is showing that known PUFs and biometrics satisfy the necessary input distribution of our constructions.

Subsequent work (Herder et al., ePrint 2014/938) increased error-tolerance by using confidence information that may be available for some PUFs and biometrics.  It may be possible to incorporate such information to our constructions to improve applicability.

### 2014-12-01 constantRate/eurocryptReviewResponse.txt

Thank you for the reviews and feedback.  We will incorporate your comments into our work.

Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
A: The second and third construction also secure different types of sources.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction allows all blocks to be determined by a single block as long as most blocks are hard to guess.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is known as a robust fuzzy extractor (Boyen et al., Eurocrypt 2004).  It is a separate question than reusability of a fuzzy extractor. Robust fuzzy extractors are easy in the random oracle model.  In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).

Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.  Is it a hard challenge to find an alternative of removing this condition? 
Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail? It would be great to gain intuition about whether these construction can be improved or not.
A: Finding "good distributions" that are obtainable in practice and support provable security is an important and fascinating research direction.  One can view our results as providing a target for biometrics and PUFs. Our constructions show promise for two reasons.

First, the second construction provides reusability regardless of alphabet size.  (It only corrects more errors than entropy on a super-constant size alphabet.)  We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).  Known fuzzy extractors provide no guarantees for irises.  However, there is still work to verify that bits sampled from an iris code have high entropy.  The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions.

Second, the constructions support different types of sources (the second construct does support a superset of the first). This provides multiple options for building a PUF or biometric transform.

Supporting more errors than entropy on a constant size alphabet remains a challenge.  As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors.  This is to avoid stronger lower bounds that arise when working on a single space.  Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.  It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.

### 2014-12-02 trunk/constantRate/eurocryptReviewResponse.txt

Thank you for the reviews and feedback.  We will incorporate your comments into our work.
We address only the most important comments below.

Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
A: The second and third construction not only add reusability--they also handle more interesting sources than the first construction, and thus are interesting even when reusability is not relevant.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is known as a robust fuzzy extractor (Boyen et al., Eurocrypt 2004).  It is a separate question than reusability of a fuzzy extractor. As Boyen et al. show, adding robustness to any fuzzy extractor (including ours) is easy in the random oracle model. In the standard model, constructions are more fragile and utilize one-time MACs (Dodis et al., Crypto 2006).

Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.  Is it a hard challenge to find an alternative of removing this condition? 
Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?

A: The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions. Finding such PUFs and biometric transforms is a fascinating research question that we are currently working on.

One can view our results as providing a target for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired. Our constructions show promise for the following reasons:

They support different types of sources. This provides multiple options for building a PUF or a biometric transform.

In particular, the second construction supports sources whose symbols are k-wise independent for a sufficient k. This means that even if the resulting string, after all the signal processing, overdefines the original signal (and thus has little entropy relative to its length), our construction may still apply.

Finally, the second construction provides reusability regardless of alphabet size (although the "more errors than entropy" claim holds only for a super-constant size alphabet).

We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).  Known fuzzy extractors provide no guarantees for irises.  However, there is still work to verify that bits sampled from an iris code have high entropy.

Q: It would be great to gain intuition about whether these construction can be improved or not.

Supporting more errors than entropy on a constant size alphabet remains a challenge.  As the reviewers note, we crucially make use of two metric spaces: the input metric and a second metric space where we correct errors.  This is to avoid stronger lower bounds that arise when working on a single space, since known techniques for working on a single space recover the original reading, and are subject to stronger negative results.  It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.

### 2014-12-02 constantRate/eurocryptReviewResponse.txt

Thank you for the reviews and feedback.  We will incorporate your comments into our work.
We address only the most important comments below.

Q: The second and third construction use obfuscation (for point functions) to add "reusability" 
A: The second and third construction not only add reusability--they also handle more interesting sources than the first construction, and thus are interesting even when reusability is not relevant.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is important, but orthogonal to the challenges addressed by this submission. Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors” (Boyen et al., Eurocrypt 2004). Boyen et al. observed that, in the random oracle model, one can make a fuzzy extractor robust without harming other properties. Conversions in the standard model are more delicate (Dodis et al., Crypto 2006). Finding robust versions of the constructions in this submission is an interesting question, but lies beyond the scope of this submission.

Q:  I would like to suggest the authors to add some detailed discussion whether the result of this work can be used in general applications, where the condition of a super-constant size of alphabet might does not naturally hold.  Is it a hard challenge to find an alternative of removing this condition? 
Q: Also the constructions are somewhat unrelated: how do they compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?

A: The main barrier to applicability is showing that known PUFs and biometrics fulfill our distributional conditions. Finding such PUFs and biometric transforms is a fascinating research question that we are currently working on.

One can view our results as providing a target for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired. Our constructions show promise for the following reasons:

They support different types of sources. This provides multiple options for building a PUF or a biometric transform.

In particular, the second construction supports sources whose symbols are k-wise independent for a sufficient k. This means that even if the resulting string, after all the signal processing, overdefines the original signal (and thus has little entropy relative to its length), our construction may still apply.

Finally, the second construction provides reusability regardless of alphabet size (although the "more errors than entropy" claim holds only for a super-constant size alphabet).

We have run initial experiments and the second construction appears promising for irises (where the distance is binary Hamming over 2048 bit strings).  Known fuzzy extractors provide no guarantees for irises.  However, there is still work to verify that bits sampled from an iris code have high entropy.

Q: It would be great to gain intuition about whether these construction can be improved or not.

Supporting more errors than entropy on a constant size alphabet remains a challenge.  As the reviewers note, we crucially make use of two metric spaces: the input metric and a second metric space where we correct errors.  This is to avoid stronger lower bounds that arise when working on a single space, since known techniques for working on a single space recover the original reading, and are subject to stronger negative results.  It is not clear how to make use of multiple metric spaces when the starting alphabet is constant size.

### 2014-12-02 constantRate/eurocryptReviewResponse.txt

Thank you for the feedback, which we will incorporate. We address most salient comments below.

Q: The second and third construction use obfuscation (for point functions) to add "reusability".
A: These constructions not only add reusability--they also handle other sources than the first construction, and thus are interesting even when reusability is not relevant.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is important, but orthogonal to the challenges addressed by this submission. Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors”; in the random oracle model, any fuzzy extractor can be made robust without harming other properties (Boyen et al., Eurocrypt 2004). Conversions in the standard model are more delicate (Dodis et al., Crypto 2006). Finding robust versions of the constructions in this submission without using random oracles is an interesting question, but lies beyond the scope of this submission.

Q: Is it a hard challenge to find an alternative [for the condition of super-constant size alphabet]?

A: Super-constant alphabet is not necessary in the second construction. For example, it supports binary sources whose symbols are k-wise independent for a sufficient k (see last sentence of 4.4). This means that even if the resulting string, after all the signal processing, overdefines the original signal (and thus has little entropy relative to its length), our construction may still apply. This construction may be useful for discretization procedures similar to ones that are used in the IrisCode (which takes the sign of each coordinate of a multidimensional continuous vector).

Q: How do the [constructions] compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?

A: As we discuss, SOME distributional conditions seem necessary, so it’s a matter of finding the magic spot for which fuzzy extractors exist and realistic sources can satisfy. Our work can be seen as providing guidance for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired. Since our constructions support different types of sources, they they provide multiple options for building a PUF or a biometric transform.

@@

Q: It would be great to gain intuition about whether these construction can be improved or not.

A: As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors. Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.

@@

Subsequent work (Herder et al., ePrint 2014/938) increased error-tolerance by using confidence information that may be available for some PUFs and biometrics.  It may be possible to incorporate such information to our constructions to improve applicability.

It may also be possible to explore which transformations can be used to change the alphabet and the distribution to get them closer to our conditions.

### 2014-12-02 trunk/constantRate/eurocryptReviewResponse.txt

Thank you for the feedback, which we will incorporate. We address most salient comments below.

Q: The second and third construction use obfuscation (for point functions) to add "reusability".
A: These constructions not only add reusability--they also handle different sources than the first construction, and thus are interesting even when reusability is not relevant.  The first construction requires many blocks to contribute fresh entropy conditioned on previous blocks (for some order of blocks).  The second construction requires that sampling produces a high entropy string (this class is larger than supported sources for the first construction).  The third construction requires most blocks to be hard to guess on their own--but permits, for example, all blocks to be determined by a single one.

Q: Missing is an answer to the question what happens if an attacker maliciously modifies helper data in order to force the extractor to output a different key.
A: This question is important, but orthogonal to the challenges addressed by this submission. Constructions that can handle malicious manipulation of the helper data are called “robust fuzzy extractors”; in the random oracle model, any fuzzy extractor can be made robust without harming other properties (Boyen et al., Eurocrypt 2004). Conversions in the standard model are more delicate (Dodis et al., Crypto 2006). Finding robust versions of the constructions in this submission without using random oracles is an interesting question, but lies beyond the scope of this submission.

Q: Is it a hard challenge to find an alternative [for the condition of super-constant size alphabet]?

A: As the reviewers note, we crucially make use of two metric spaces, the input metric and a second metric space where we correct errors. Known techniques for working on a single space recover the original reading, known as a secure sketch, and are subject to stronger negative results.  The two metric space technique is most applicable for super-constant size alphabet.

However, super-constant alphabet is not necessary in the second construction. For example, it supports binary sources whose symbols are k-wise independent for a sufficient k (see last paragraph of 4.4).

Q: How do the [constructions] compare in terms of the classes of sources they work for, how do they apply to those sources (biometric, PUF examples) where standard fuzzy extractors fail?

A: As we discuss, some distributional conditions seem necessary, so it’s a matter of finding a condition where secure fuzzy extractors exist that realistic sources satisfy. Our work can be seen as providing guidance for the way biometrics should be measured and PUFs should be designed if fuzzy extractors are desired. Since our constructions support different types of sources, they they provide multiple options for building a PUF or a biometric transform.

For example, the IrisCode transform takes the sign of Gabor filters at nearby locations so the resulting signal is likely redundant.  This redundancy makes existing constructions fail (as the source is far from uniform).  However, the produced binary vector may satisfy the k-wise independence condition necessary for the second construction.

### 2014-12-17 trunk/info-bounds/FuzzyExtPossibility.tex
MIT CIS talk
adding discussion of correlated random variables

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL\mhyphen rlx}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\unprlx}{\ensuremath{\mathtt{unp\mhyphen rlx}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
\newcommand{\Huse}{\mathrm{H}_{\mathtt{usable}}}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
  University and MIT Lincoln Laboratory.}  \and Leonid
Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
  Pennsylvania State University. A.S. is supported NSF awards
  \#0747294 and \#0941553. This work performed while visiting Boston
  University's Hariri Institute for Computing.}}
}
\begin{document}
\maketitle

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.

@@

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy. % We now describe the known distribution setting.

%\subsection{Known Distribution Algorithms}
%\label{sec:known distributions def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
%We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
%
%\begin{definition}
%Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution %secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
%\begin{enumerate}
%\item \emph{Correctness:} 
%$
%\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
%Correctness is guaranteed only for the support of $W$.
%\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
\label{sec:family of dist}

@@

\section*{Acknowledgements}
The authors are grateful to Gene Itkis and Yevgeniy Dodis for helpful discussions.
The work of Benjamin Fuller is sponsored in part by US NSF grants 1012910 and 1012798 and  the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government. 
Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.

>>>>

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL\mhyphen rlx}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\unprlx}{\ensuremath{\mathtt{unp\mhyphen rlx}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Hfuzz}{\mathrm{H}^{\mathtt{fuzz}}_{t,\infty}}
\newcommand{\Hcorr}{\mathrm{H}^{\mathtt{corr}}}
\newcommand{\Huse}{\mathrm{H}_{\mathtt{usable}}}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
  University and MIT Lincoln Laboratory.}  \and Leonid
Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
  Pennsylvania State University. This work performed while visiting Boston
  University's Hariri Institute for Computing.}}
}
\begin{document}
\maketitle

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \secref{sec:known distributions}.

@@

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.

\paragraph{Generalizing to correlated random variables}
Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.  They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.  A random variable has smooth entropy if it is statistically close to a distribution with true entropy. We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.  We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]

Furthermore, they show there exists a protocol with this length $p$ using optimal encoding functions.  Intuitively, the public information must describe which possible outcome for $W$ actually occurred. This result describes the maximal length of $p$ and does not argue how $p$ effects security.  It may be possible to construct a $p$ that reduces the entropy of $w$ by less than $\log |p|$.  In \secref{sec:known distributions}, we will construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.

Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.  We compare this characterization to fuzzy min-entropy in \secref{sec:known distributions}.

Fuzzy min-entropy can be generalized to this setting.   Fuzzy extractors consider the worst case $w'$.  When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.  In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.  Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.  In this work, we consider worst case correctness and use unsmoothed entropy.}

\begin{definition}
\label{def:cor fuzz min}
Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
\end{definition}
\noindent 
In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
For now, we consider sufficiency of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}). We then consider the implications of our results on the correlated reading setting (\defref{def:cor fuzz min}).

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.

\paragraph{Connection to the characterization of~\cite{DBLP:conf/asiacrypt/RennerW05}}
Renner and Wolf characterize when it is possible to derive keys from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.  They consider all possible (randomized) transforms $T, T'$ of $W, W'$ into a new pair of variables $V,V'$.  They show that \[|\key| \le \sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).\]  Furthermore, they show that there is a transformation that achieves a key of nearly this length.  The result is nonconstructive as there is no guidance on how to find the transforms $T, T'$.  Since there is no known bound on the length of $T, T'$ it is not clear how to search the transform space even with unlimited time.
\consref{cons:leveling} can be used to derive keys from correlated random variables.  The main change is to define \[W^* = \{w | \Pr[W=w | W'=w'] >0 \wedge \Pr[W=w]\in L_i\}.\]  
Our result shows if one is satisfied with obtaining a strong key when possible (our protocol has losses of $2\log 1/\epsilon + \log n+\log 1/\delta$), then a protocol is possible (and explicitly constructible) in the original space.

\section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
\label{sec:family of dist}

@@

\section*{Acknowledgements}
The authors are grateful to Gene Itkis and Yevgeniy Dodis for helpful discussions.
The work of Benjamin Fuller is sponsored in part by US NSF grants 1012910 and 1012798 and  the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government. 
Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.  Adam Smith is supported in part by NSF awards 0747294 and 0941553.
